\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\usepackage{comment}
\graphicspath{{./}{./images/}}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

\newcommand{\cf}{\textit{cf.} } 
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }

\begin{document}

\title{Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface}
 
\author{Tianci Zhou}
\email{tzhou13@illinois.edu}
\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}

\author{Mao Lin}
\email{maolin2@illinois.edu}
\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}

\date{\today}

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}
\input{intro}

\section{Bosonic Conformal Interface}
\subsection{General Formulation}
\label{sec_sub:general_formulation}
\input{general_formulation}
% M, S
% special case
\subsection{A Free Boson Lattice Model}
\label{sec_sub:free_boson_lattice}
% cite Calabrese, introduce the model
% lattice model S matrix
\input{free_boson_lattice}

\section{Bipartite Fidelity and Loschmidt Echo}
\subsection{Definition}
% definition
% general discussion

\section{Analytic and Numerical Results}
\label{sec:analytic_numerics}
\subsection{Fidelity}
% analytic: conformal transformation
% numerical comparison
\subsection{Loschmidt Echo}
% analytic: conformal transformation
% numerical comparison

\section{Discussion}

% connecting Luttinger liquid(quantum wire) using votage to control the boundary condition. X-ray edge singularity. examples include Taylor santo's topological phases. Hope to have experimental setup. 

There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides. 

\begin{acknowledgments}
\todo[inline]{Thomas Faulkner, Xueda Wen, Shinsei Ryu, Romain Vasseur}
    TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
    This work made use of the Illinois Campus Cluster, a computing resource that is operated by the
    Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for
    Supercomputing Applications (NCSA) and which is supported by funds from the University of
    Illinois at Urbana-Champaign.
\end{acknowledgments}

\appendix
\section{Corrections to the Free Energy}
% two corrections:
% 1. staircase geometry
% 2. contribution from the boundary: cite Cardy 
\label{app:F_correction}
\input{F_correction}

\section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
% basis transformation, Bogoliubov state, overlap(master theorem)
% Peschel_EE.pdf
\label{app:comp_fid_echo}
\input{comp_fid_echo}

\section{A Determinant Identity for the Boundary State Amplitude}
\label{app:pf_of_id}
% copy notes app. C
\input{pf_of_id}

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
\label{app:gnd_dn_lambda}
% copy notes app. A
\input{gnd_dn_lambda}

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
\label{app:lambda_12}
% copy notes app. B
\input{lambda_1_lambda_2}

\section{Winding Modes of Compact Bosons}
% free boson + compact
\label{app:compact_diff_boson}
\input{compact_boson}

\bibliographystyle{plain}
\bibliography{bCFT}

\end{document}

%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End: 
